MSB205 - Boligmarkedsøkonomi og anvendt spatial økonometri

### 2021-11-08 MSB205_King_County_Silje_Sofie_Karl-Gunnnar.Rmd
datasett koblet sammen mandagsarbeid

```{r}
asc_b19101_fam_inc <- read.dbf("maps/censusSHP/acs_b19101_familyincome.dbf")
```

>>>>

```{r}
kc_wadoh_map <- here("maps/WADOH_Environmental_Health_Disparities_Index_Calculated_for_King_County___wadohehdindex_area/WADOH_Environmental_Health_Disparities_Index_Calculated_for_King_County___wadohehdindex_area.shp") %>% 
      st_read() %>% 
  st_transform(2926)
```

```{r}
kc_wadoh_map <- kc_wadoh_map %>% 
  select(
  GEO_ID_TRT,
  EHD_percen,#Environmental Health Index, weighted score many vars
  linguist_2,#Pop. age 5+ speaking English less than "very well"
  poverty_pe,#Percentage people living in poverty
  POC_percen,#People of Color in percentage of pop. in tract
  transporta,#% of income spent on transportation median family in tract
  unemploy_2,#percentage unemployed
  housing_pe,#% of households in group "Unaffordable Housing" (>30% inc.)
  traffic_pe,#% of pop. near heavy traffic roadways
  diesel,# nox consentration
  ozone,# ozone consentration
  PM25, # consentration of Particulate Matter in air
  toxic_rele, # Toxic release from factories
  hazardous_, # Hazardous Waste Treatment Storage and disposal Facilities
  lead_perce, # measure of Lead paint in houses
  superfund, # Proximity to contaminated sites on national list
  facilities, # Proximity to Risk Management Plan Facilities
  wastewater, # Proximity to wastewater facilities
  sen_pop_pe, # % pop. over 65
  socio_perc # score social economic determants, low best
  )
```

```{r}
class(kc_wadoh_map)
```

```{r}
asc_b19101_fam_inc <- read.dbf("maps/censusSHP/acs_b19101_familyincome.dbf")
attach(asc_b19101_fam_inc)
```

```{r}
asc_b19101_fam_inc <- asc_b19101_fam_inc %>% 
    mutate(low = (E19101138 + E19101139 + E19101140 + E19101141 + E19101142 + E19101143)) %>% 
    mutate(mid = (E19101144 + E19101145 + E19101146 + E19101147 + E19101148 + E19101149)) %>% 
    mutate(high = (E19101150 + E19101151 + E19101152 + E19101153))
```

```{r}
asc_b19101_fam_inc <- asc_b19101_fam_inc %>% 
    select(GEOIDTRT, low, mid, high) %>% 
    rename(GEO_ID_TRT = GEOIDTRT)
```

```{r}
kc_wadoh_map_2 <- left_join(
    asc_b19101_fam_inc,
    st_drop_geometry(kc_wadoh_map),
    by = "GEO_ID_TRT")
```

```{r}
class(kc_wadoh_map_2)
```

```{r}
kc_tracts10 <- here("maps/censusSHP/tracts10.shp") %>% 
  st_read() %>% 
  st_transform(2926)
```

```{r}
kc_tracts10_shore <- here("maps/censusSHP/tracts10_shore.shp") %>% 
  st_read() %>% 
  st_transform(2926)
```

```{r}
kc_tracts10_env_data <- left_join(
  kc_tracts10, kc_wadoh_map_2,
  by = "GEO_ID_TRT"
  )

kc_tracts10_shore_env_data <- left_join(
  kc_tracts10_shore, kc_wadoh_map_2,
  by = "GEO_ID_TRT"
  )
```

```{r}
class(kc_tracts10_env_data)
class(kc_tracts10_shore_env_data)
```

```{r}
summary(kc_tracts10)
```

```{r}
kc_houses_env_var <- st_join(kc_house_data_sf, kc_tracts10_env_data)
```

```{r}
st_write(kc_houses_env_var, "kc_houses_env_var.gpkg", append = FALSE)
```
